### 2022-04-12 README.Rmd
address pkgdown warnings
* vignette metadata
* use hex included in built package for pkgdown site

# infer R Package <img src="figs/infer_gnome.png" align="right" width=280 />

@@

```{r load-package, echo = FALSE, message = FALSE, warning = FALSE}
library(devtools)
devtools::load_all()
```

>>>>

# infer R Package <img src="man/figures/infer.png" align="right" width=280 />

@@

```{r load-package, echo = FALSE, message = FALSE, warning = FALSE}
library(infer)
```
